---
title: "Homework 1"
subtitle: "Introduction to R for Public Health and Biomedical Research"
author: "Enter your name here"
date: "Enter the date here"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Part 1: Debugging

Find and correct the 10 mistakes in the code below.

```{r eval = FALSE}
x -> 10
y -> 5

x + Y

# vector of numeric values 4, 3.5 and 6
z <- C(4, 3.5, "6") 
is.numeric{Z}

w <- 1;7 # vector of whole numbers one to seven

# Character vector of fruits
Fruits <- c("Banana", "grape", "apple")
fruits == "banana" # logical, should be true where fruits are "banana"

sample(x = c(0,1), size = 5, replace = true)
Rnorm(10) # sample of the standard normal distribution of size 10
```


## Part 2: Creation of variables and assignment of values

Create a variable `x` that contains the vector of the numbers 10 to 3. What is the type of `x`?

```{r}
# Enter code here.
```

Create a variable `pets` that contains a vector with the values dog, goldfish and cat. 

```{r}
# Enter code here.
```

What is the type of `pets`?

```{r}
# Enter code here.
```

Draw a sample with replacement of sample size 10 from `pets`. Call your sample `mypets`. Use the seed `123`. Apply the factor function to `mypets` and save the result to `mypets`.

```{r}
# Enter code here.
```

Print the summary of `mypets`.

```{r}
# Enter code here.
```


### Extra Point:

Answer the question: How many cats are included in mypets?

*Write your answer here.*

