---
title: "Class Exercise 1"
author: "Your Name"
date: "2/13/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Exercise 1

Create a variable `z` and assign it the value 10: 

```{r}

```

Create a vector variable `x` and assign it the vector of numbers from one to ten. 

```{r}

```

Calculate the sum and the mean of `x`.

```{r}

```

Compare the data structure of `x` and `z` using the `str` function on each variable.

```{r}

```


## Exercise 2

Use a comparison operator to check whether the sum of the first 10 natural numbers is larger than or equal to 50.

```{r}

```

Use a comparison operator to check whether the sum of the first 100 numbers is larger than or equal to 5000.

```{r}

```

## Exercise 3

1. Create a new variable `fruitbasket` that contains a random sample of size 10 from the vector `fruit` with replacement.
2. Use a comparison operator to calculate the number of bananas in the fruit basket.

```{r}
set.seed(123)
fruit <- c("banana", "peach", "cherry")

# Add code here
```


## Exercise 4

Use a comparison operator to check whether for a random natural number `n`, the sum of the first n is larger than or equal to `n*(n-1)/2`.

```{r}

```

## Exercise 5

Create a random sample from a standard normal distribution of size 100. 

1. What percentage of values is larger than zero?
2. What percentage of values is smaller than zero?
3. What percentage of values is larger than the standard deviation of the sample?

```{r}

```

